An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-28 paper/paper.tex
Paper: Add the username/password section to the Future Work section

@@

\subsection{Challenge Mechanism} \label{subsec:ChallengeMechanism_sec:Fairness_chap:BTBackup}
% TODO: Fix this section so that it talks about the new challenge mechanism.
Even though the technique described above allows peers to find nodes with a sufficient amount of storage space, it does not guarantee that the node will keep its promise and actually store the data. For instance, a node can accept a peer's data, only to discard it immediately. A peer will only find out that its data has been discarded when it needs to retrieve backups, at which point it is too late.

To combat this, we have designed a challenge system that forces nodes to prove that they are actually storing the data that they are claiming to store. This system is based on the mechanism used in PeerStore \cite{PeerStore}. A challenge in our system consists of a randomly-generated salt followed by a specified range of bytes in the file being backed up. The node holding the peer's data must take the bytes in the specified range, hash it using the provided salt, and return the result to the peer. The peer is able to test whether the answer is correct by encrypting the file in the same way as it is stored on the node and hashing the byte range + salt accordingly. If the correct answer is returned, then the node has passed the challenge. If the node does not respond or gives the wrong answer, the challenge has been failed. By choosing a random subset of bytes and by using a salt, the node cannot calculate the hash ahead of time and only store that; the whole file must be stored in order to be able to successfully complete all possible challenges.

@@

>>>>

\subsubsection{Data Recovery}
\label{subsubsec:DataRecovery_sec:DataExchange_chap:BTBackup}
In order for this system to be useful, there needs to be a method of recovering one's data after a computer failure. To do this in our system, each peer needs to keep track of a minimal amount of data. This includes the peer's ID, so that it can be reintegrated into the system, and information on each file being backed up. For each file, the encryption keys and the addresses of each node that that has a replica needs to be stored. The peer needs to keep track of this information file through some other means. In the future work section, we describe a simple mechanism to extend our system, where this information file could be stored in the system itself.

@@

\subsection{Challenge Mechanism} \label{subsec:ChallengeMechanism_sec:Fairness_chap:BTBackup}
% TODO: Fix this section so that it talks about the new challenge mechanism.
Even though the technique described above allows peers to find nodes with a sufficient amount of storage space, it does not guarantee that the node will keep its promise and actually store the data. If no one is there to make sure that the promise to store data is kept, a malicious node could trick peers into thinking that it is storing more data than it actually is. This would be simple to accomplish; a node only has to accept data over the network but not actually store it. A peer will only find out that its data has been discarded when it needs to retrieve backups, at which point it is too late.

To solve this problem, we have designed a challenge system that forces nodes to prove that they are actually storing the data that they are claiming to store. This system is based on the mechanism used in PeerStore \cite{PeerStore}. A challenge in our system consists of a randomly-generated salt followed by a specified range of bytes in the file being backed up. The node holding the peer's data must take the bytes in the specified range, hash it using the provided salt, and return the result to the peer. The peer is able to test whether the answer is correct by encrypting the file in the same way as it is stored on the node and hashing the byte range + salt accordingly. If the correct answer is returned, then the node has passed the challenge. If the node does not respond or gives the wrong answer, the challenge has been failed. By choosing a random subset of bytes and by using a salt, the node cannot calculate the hash ahead of time and only store that; the whole file must be stored in order to be able to successfully complete all possible challenges.

@@

% TODO: I might just be guessing on the password hash as a key part. Does this actually work?
\subsection{Local Backup Information File Storage}

In section \ref{subsubsec:DataRecovery_sec:DataExchange_chap:BTBackup}, we explained that it would be possible to backup the metadata that allows a peer to find its backups. We believe that it could be possible to do this within BTBackup itself, which would eliminate the need to use some other means of safekeeping the data, such as another backup service or storing it on some other physical media. To do this, a simple username and password system could be added to the metadata layer. In a system like this, the node ID could be a hash of the chosen username, rather than one generated randomly or by IP address. The backup information file would then be stored with that user's metadata. In a system implemented with a DHT, this information would have to be encrypted, since it would be easy for the node holding that information to read it. This could be accomplished by hashing the user's chosen password and using the hash as the encryption key. This way, the only person who can read the information is the one who it belongs to. In this case, the only information that needs to be remembered by each user is his or her username and password. This is reasonable, as many modern applications have a username/password system.
